### 2022-07-01 paper/main.tex
more on bnrw

\par While Urban Areas are an effective method of measuring the true sizes of cities, they are difficult to map and obtain statistics on. Their shapes are generally compact and do not have any sort of uniform, governing body. To alleviate these issues, we choose Metropolitan Statistical Areas (MSAs) as our scale. MSAs consist of the county or counties in which an Urban Area lies, alongside any counties in which 25\% of the population commutes to a core county (REF). In this way, we gain the population measurement accuracy of UAs with the ease of data access from state-defined municipalities. MSAs also lump together similar, nearby cities, such as New York, Newark, and Jersey City, to avoid redundant analysis. As of March 2020, there are 384 Metropolitan Statistical Areas, each with a corresponding Reddit community (REF).

\section{Traditional Media}
\par TODO: papers about historical media and crime, modern issues, social media effects

@@

@@

\begin{figure}[ht]
    \includegraphics[width=0.75\textwidth]{Images/timeline.pdf}
    \caption{Number of daily posts across all subreddits}
    \label{fig:line-1}
\end{figure}

>>>>

\par While Urban Areas are an effective method of measuring the true sizes of cities, they are difficult to map and obtain statistics on. Their shapes are generally compact and do not have any sort of uniform, governing body. To alleviate these issues, we choose Metropolitan Statistical Areas (MSAs) as our scale. MSAs consist of the county or counties in which an Urban Area lies, alongside any counties in which 25\% of the population commutes to a core county (REF). In this way, we gain the population measurement accuracy of UAs with the ease of data access from state-defined municipalities. MSAs also lump together similar, nearby cities, such as New York, Newark, and Jersey City, to avoid redundant analysis. As of March 2020, there are 384 Metropolitan Statistical Areas (REF), each with a corresponding Reddit community.

\section{Traditional Media}

% REFS:
% https://books.google.com/books?id=BmwuDwAAQBAJ&lpg=PP1&ots=_PlVBghHER&dq=media%20and%20crime&lr&pg=PP1#v=onepage&q=media%20and%20crime&f=false
% https://doi.org/10.1177/0002716295539001011
% https://doi.org/10.1177/0002764296039004003
% https://doi.org/10.1177/19401612211020929
% https://www.cambridge.org/core/books/television-and-its-viewers/83C017F8F8416B5D5F2716EBE5D354BF
% http://personal.psu.edu/exs44/597b-Comm&Crime/Wilson-Kelling-Broken%20Windows.pdf
% https://researchgate.net/profile/Tracey-Meares-2/publication/268224149_The_Law_and_Social_Science_of_Stop_and_Frisk/links/54665ea60cf25b85d17f6112/The-Law-and-Social-Science-of-Stop-and-Frisk.pdf
% https://oxford.universitypressscholarship.com/view/10.1093/acprof:oso/9780195369083.001.0001/acprof-9780195369083

\par Traditional media, such as television, newspapers, magazines, and radio, have long been intertwined with a fascination for crime. Live manhunts for people such as OJ Simpson (REF 1) and the Boston Bombers (REF ?) have captured and enthralled viewers and readers. However, while high-profile cases garner much of the attention, local and lower-profile cases often inhabit newspaper columns and television segments. It is with these cases that people grow uneasy with the sense of public safety in their community. A flurry of reporting on violent acts can increase worry, stress, and fear that crime is rising, even if the documented crime statistics show that crime has not increased (REF 3).

\par An increase in a fear of crime can have implications beyond elevated negative emotions. Fear of crime has far-reaching political social (REF 1), (REF ?), and institutional (REF 2) impacts. Belief in excessive amounts of crime can lead to loss of community cohesion (REF 3). (REF 3) found that as television news media consumption increased, distrust both in the local community and the world ``out there'' increased. Additionally, media creators often sensationalized stories, turning unfortunate incidents into grim spectacles. Those that perceived crime to be worse than others were more likely to perform excessive crime prevention actions, such as not leaving their house or engaging with the neighborhood.

\par (REF 4) describes how the prevalence of crime discussion affected the 2016 presidential election in the United States. The authors found that voters who consumed more television in turn consumed more campaign advertisements, of which many were about issues such as crime and violence. Frequent crime media consumers predict crime and violence issues to be worse than they really are (REF 5). Furthermore, the authors found that excessive crime reporting and media exposure had impacts on voting patterns; those that believed crime to be worse tended to vote for more conservative candidates.

\par Worry of crime victimization can lead to the creation of institutional policies meant to combat the perceived threat. One notable example is the idea of Broken Windows Theory (REF 6) and a practice that stemmed from its development, known as stop and frisk (REF 7). Broken Windows Theory states that visible signs of crime and disorder lead to further crimes and disorder (REF 6). Essentially, the theory states that ignoring minor criminal incidents can lead to more frequent and serious issues. Acting on this theory, the New York Police Department instituted a stop and frisk policy, in which police officers temporarily detained civilians suspected of carrying illegal objects (REF 7). The effectiveness of the policy, while believed to be effective at the time, has since come under scrutiny. Researchers found that only 6\% of stops resulted in arrests (REF 7) and that there is no clear proof that stop and frisk contributed to the decline in crime in New York City (REF 8). Stop and frisk was removed as a policy in 2013 when it was deemed unconstitutional (REF 7).

@@

\subsection{Social Media and Crime}

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.75\textwidth]{Images/timeline.pdf}
    \caption{Number of daily posts across all subreddits}
    \label{fig:line-1}
\end{figure}
